A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-17 main.tex
Fix abstract with grammarly.

Dependent types are types dependent on values. 
Vectors with lengths are a famous example of dependent types and they enable us to omit boundary checking.

@@

It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
It also includes an evaluation context which satisfies unique decomposition.

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
Especially, handling CSP in equivalence rules of dependent types wasn't clear.
Parameters of dependent types may contain cross-staged terms.
We give reasonable equivalence rules to handle them.

@@

\blue{213 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}

>>>>

Dependent types are types dependent on values. 
A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.

@@

\LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
It also includes an evaluation context which satisfies unique decomposition.

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
In this paper, we give reasonable equivalence rules to handle them.

@@

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}
